---
title: 'NRSG 741: HW_01'
author: "TommY Flynn"
date: "1/26/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
GitHub Repository @ [https://github.com/tommyflynn/N741_Homework.git](https://github.com/tommyflynn/N741_Homework.git)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gapminder)
library(ggplot2)
library(dplyr)
library(knitr)
```
## Task One:
The mean life expectancy is `r round(mean(gapminder$lifeExp), digits = 2)` years,
with a standard deviation of `r round(sd(gapminder$lifeExp), digits = 2)`, median of `r round(median(gapminder$lifeExp), digits = 2)`, and sample size of `r length(gapminder$lifeExp)`.


## Task Two:
```{r, echo = TRUE}
kable(gapminder %>% 
  group_by(Continent = continent) %>%
  summarise(LE_median = median(lifeExp), LE_sd = sd(lifeExp), 
            LE_mean = mean(lifeExp)), caption = "Life Expectancy by Continent: Summary Statistics"
)
```

##Task Three:  
```{r , echo = TRUE}
contXlife <- ggplot(gapminder, aes(x = continent, y = lifeExp))
contXlife + geom_boxplot(fill = "yellow", colour = "blue", outlier.colour = "hotpink") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4) + 
  labs(x="Continent", y="Life Expectancy", title="Boxplot of Life Expectancy by Continent")
```
  
```{r, echo=TRUE}
contXgdp <- ggplot(gapminder, aes(x = continent, y = log(gdpPercap)))
contXgdp + geom_boxplot(fill = "hotpink", colour = "yellow", outlier.colour = "blue") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4) + 
  labs(x="Continent", y="LogGDP per capita", title="Boxplot of Per Capita GDP by Continent")
```
    
```{r, echo = TRUE}
contXpop <- ggplot(gapminder, aes(x = continent, y = pop)) 
contXpop + geom_boxplot(fill = "black", colour = "red", outlier.colour = "yellow") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4) + 
  labs(x="Continent", y="Population", title="Boxplot of Population by Continent")

```
 
## Task Four:  
**Scatterplot of countries in Asia and the Americas according to per capita GDP and life expectancy (country nodes scaled to population)**  
```{r, echo = TRUE}
colorful_gap <-
  data.frame(gapminder,
             cc = I(country_colors[match(gapminder$country,
                                         names(country_colors))]))
Continent <- with(colorful_gap, continent %in% c("Americas", "Asia") & year == 1992)
plot(lifeExp ~ gdpPercap, colorful_gap, subset = Continent, log = "x", pch = 21, 
     cex = sqrt(colorful_gap$pop[Continent]/pi)/1500, bg = colorful_gap$cc[Continent])
```  


**References**    
1. Jennifer Bryan (2017). gapminder: Data from Gapminder. R package version 0.3.0.
https://CRAN.R-project.org/package=gapminder