---
title: 'NRSG 741: HW_01'
author: "TommY Flynn"
date: "1/26/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
Click link for [GitHub Repository](https://github.com/tommyflynn/N741_Homework.git)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gapminder)
library(ggplot2)
library(dplyr)
library(knitr)
```
##Task One:
The mean life expectancy is `r round(mean(gapminder$lifeExp), digits = 2)` years,
with a standard deviation of `r round(sd(gapminder$lifeExp), digits = 2)`, median of `r round(median(gapminder$lifeExp), digits = 2)`, and sample size of `r length(gapminder$lifeExp)`.[^1]


##Task Two:
```{r, echo = FALSE}
kable(gapminder %>% 
  group_by(Continent = continent) %>%
  summarise(LE_median = median(lifeExp), LE_sd = sd(lifeExp), LE_mean = mean(lifeExp)), caption = "Life Expectancy by Continent: Summary Statistics"
)
```

##Task Three:
####Life Expectancy by Continent
```{r}
contXlife <- ggplot(gapminder, aes(x = continent, y = lifeExp))
contXlife + geom_boxplot(fill = "yellow", colour = "blue", outlier.colour = "hotpink") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```
####Gross Domestic Product by Continent
```{r}
contXgdp <- ggplot(gapminder, aes(x = continent, y = gdpPercap))
contXgdp + geom_boxplot(fill = "hotpink", colour = "yellow", outlier.colour = "blue") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```
####Population by Continent
```{r}
contXpop <- ggplot(gapminder, aes(x = continent, y = pop))
contXpop + geom_boxplot(fill = "black", colour = "red", outlier.colour = "yellow") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```

##Task Four:

**References**
[^1]: Jennifer Bryan (2017). gapminder: Data from Gapminder. R package version 0.3.0.
https://CRAN.R-project.org/package=gapminder