---
title: "Homework 2: NRSG 741"
author:
  - name: Tommy Flynn
    email: tjflynn@emory.edu
    affiliation: Emory University
    footnote: Corresponding Author
address:
  - code: Emory University
    address: Emory School of Nursing 1520 Clifton Rd Atlanta GA 30322
abstract:  |
  This assignment applies the dplyr and ggplot2 packages to work with the   Davis dataset in the car package, which contains data on the measured   and reported heights and weights of men and women engagedin regular exercise. The associated GitHub repository can be found at <https://github.com/tommyflynn/N741_Homework/tree/master/Flynn_HW_02>.

output: 
  rticles::elsevier_article:
    latex_engine: xelatex
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(warnings = TRUE)
knitr::opts_chunk$set(message = TRUE)
library(tidyverse)
library(car)
library(quantreg)
library(janitor)
davis <- car::Davis
```
##### 1. What kind of R object is the Davis dataset?
> Answer: The Davis dataset is the "`r paste(class(davis))`" class of R object.

##### 2. How many observations are in the Davis dataset?
> Answer: There are `r paste(count(davis))` observations. 

```{r missing}
#Use the is.na function to filter non-missing values from the repwt variable
repmissing <- filter(davis, is.na(repwt))
#count(repmissing)
```
##### 3. For reported weight, how many observations have a missing value?
> Answer: Reported weight has `r count(repmissing)` missing values

##### 4. How many observations have missing values?
```{r complete obs}
#HINT: find the complete rows...
completeobs <- count(na.omit(davis))
```
> Answer: The Davis dataset has `r completeobs` complete observations.

##### 5. Create a subset containing only females. How many females are in this subset?
```{r female subset}
femaleset <- davis %>%
  subset(sex == "F")
```
> Answer: A subset containing only females from the Davis data has `r count(femaleset)` observations. 

##### 6. What is the average BMI for these individuals?
```{r, unit transformation}
davisBMI <- davis %>%
  mutate(sqrmetHT = (height/100)*(height/100)) %>%
  mutate(BMI = weight/sqrmetHT) %>% 
  mutate(BMIclass = if_else(BMI < 18.5, "Underweight", 
                            if_else(BMI < 25.0, "Normal",
                                    if_else(BMI < 30, "Overweight",
                                            "Obese", "Missing"), 
                                    "Missing")))
#mean(davisBMI$BMI)
```
> Answer: The mean BMI is `r mean(davisBMI$BMI)`.



