---
title: "Homework 2: NRSG 741"
author:
  - name: Tommy Flynn
    email: tjflynn@emory.edu
    affiliation: Emory University
    footnote: Corresponding Author
address:
  - code: Emory University
    address: Emory School of Nursing 1520 Clifton Rd Atlanta GA 30322
abstract:  |
  This assignment applies the dplyr and ggplot2 packages to work with the   Davis dataset in the car package, which contains data on the measured   and reported heights and weights of men and women engagedin regular exercise. The associated GitHub repository can be found at <https://github.com/tommyflynn/N741_Homework/tree/master/Flynn_HW_02>.

output: 
  rticles::elsevier_article:
    latex_engine: xelatex
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(warnings = TRUE)
knitr::opts_chunk$set(message = TRUE)
library(tidyverse)
library(car)
library(quantreg)
library(janitor)
```
Using dplyr
===========
##Questions 1 & 2:

```{r, describing davis}
#1. What kind of R object is the Davis dataset?
davis <- car::Davis
#to print class inline, use `r paste(class(davis))`

#2. How many observations are in the Davis dataset?
#Q2: to print number of observations, use `r count(davis)`
```
> Answer 1: The Davis dataset is the "`r paste(class(davis))`" class of R object.

> Answer 2: There are `r paste(count(davis))` observations. 

##Question 3:

```{r missing}
#3. For reported weight, how many observations have a missing value?
#Use the is.na function to filter non-missing values from the repwt variable, then show inline with `r count(repmissing)`
repmissing <- filter(davis, is.na(repwt))
```
> Answer: Reported weight has `r count(repmissing)` missing values

##Question 4:

```{r complete obs}
#4. How many observations have missing values?
#HINT: find the complete rows... then show inline with `r completeobs`
completeobs <- count(na.omit(davis))
```
> Answer: The Davis dataset has `r completeobs` complete observations.

##Question 5:

```{r female subset}
#5. Create a subset containing only females. How many females are in this subset?
#create a subset of all female obs, print #obs inline with `r count(femaleset)
femaleset <- davis %>%
  subset(sex == "F")
```
> Answer: A subset containing only females from the Davis data has `r count(femaleset)` observations. 

##Question 6:

```{r, unit transformation}
#6. What is the average BMI for these individuals?
#create a new data.fram with height unit transformation (cm -> m), calculated BMI, and categorized BMI.
davisBMI <- davis %>%
  mutate(sqrmetHT = (height/100)*(height/100)) %>%
  mutate(BMI = weight/sqrmetHT) %>% 
  mutate(BMIclass = if_else(BMI < 18.5, "1. Underweight", 
                            if_else(BMI < 25.0, "2. Normal",
                                    if_else(BMI < 30, "3. Overweight",
                                            "4. Obese", "Missing"), 
                                    "Missing")))
#Print for Q6 inline with, `r mean(davisBMI$BMI)`
```
> Answer: The mean BMI is `r mean(davisBMI$BMI)`.

##Question 7:

```{r frequency table for BMI class}
#7. How do these individuals fall into the BMI categories (what are the frequencies and relative %’s)?
#Use janitor tably() and knitr kable() functions to make it pretty
davisBMI %>%
  janitor::tabyl(BMIclass) %>%
  knitr::kable()
```

Graphs with ggplot2
===================

##Question 8:

```{r histogram BMI}
#8. Create a histogram of BMI.
davisBMI %>%
  filter(!is.na(BMI)) %>%
  filter(BMI < 50) %>%
  ggplot(aes(BMI)) + 
  geom_histogram(colour = "black", fill = "yellow", position = "dodge", binwidth = 1) +
  geom_vline(aes(xintercept = mean(BMI, na.rm=T)), colour = "red", linetype = "dashed", size = 1) 
  
```

##Question 9:

```{r Boxplots of BMI by sex}
#9. Create side-by-side boxplots of BMI distribution by gender.
davisBMI %>%
  filter(BMI < 50) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(sex)) %>%
  ggplot(aes(x=sex, y=BMI, fill=sex)) + geom_boxplot() + guides(fill=FALSE)
```

##Question 10: 

```{r clustered bar chart}
davisBMI %>%
  filter(BMI < 50) %>%
  filter(!is.na(BMIclass)) %>%
  filter(!is.na(sex)) %>%
  ggplot(aes(BMIclass, fill = sex)) + 
  geom_bar(position = "dodge") + 
  scale_fill_brewer(palette = "Set1")
```


THE END
=======