---
title: "Flynn_HW_05"
author: "TommY"
date: "3/8/2018"
output: html_document
---
Find the repository for this assignment on GitHub by navigating to <https://github.com/tommyflynn/N741_Homework/tree/master/Flynn_HW_05>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load all packages
library(phyloseq)
library(ggplot2) 
library(RColorBrewer)
# Load dataset by pointing to its file location
load("./HMPv35.RData")
```

```{r data summary, echo=FALSE}
packageVersion("phyloseq")
packageVersion("ggplot2")
packageVersion("RColorBrewer")
HMPv35
```

####Problem 1

Subset the HMPv35 object to obtain only the samples from Tongue_dorsum. Call this new object HMPv35sub2

```{r subset, echo=TRUE}
# Fill in your code to subset
sub <- get_variable(HMPv35, "HMPbodysubsite") %in% c("Tongue_dorsum")
sample_data(HMPv35)$sub <- factor(sub)
# Call the new object HMPv35sub2
HMPv35sub2 <- prune_samples(sample_data(HMPv35)$sub == TRUE, HMPv35)
summary(sample_data(HMPv35sub2))
```


####Problem 2

Produce the geometric box plot of diversity measures for your object, HMPv35sub2
```{r answer 2}
theme_set(theme_bw())
#The following commands plot the different diversity measures for the two different body sites.
alpha_meas = c("Observed", "Chao1", "ACE", "Shannon", "Simpson", "InvSimpson")
plot_richness(HMPv35sub2, "HMPbodysubsite", measures=alpha_meas) + geom_boxplot(data=p$data, aes(x=HMPbodysubsite, y=value), alpha=0.1)
```


####Problem 3

You see what taxa are most prevalent in your subset, HMPv35sub2

```{r}
ntaxa(HMPv35sub2)
par(mar = c(10, 4, 4, 2) + 0.1) 
N <- 20
barplot(sort(taxa_sums(HMPv35sub2), TRUE)[1:N]/nsamples(HMPv35sub2), las=2)
```



####Problem 4

Using your HMPv35sub2 object, throw the rare taxa out of that object, then reduce to only taxa in the phylum Bacteroidetes. Call this new object HMPv35sub2frbac 

```{r rare taxa removal}
HMPv35sub2sub = filter_taxa(HMPv35sub2, function(x) sum(x > 3) > (0.2*length(x)), TRUE)
HMPv35sub2sub
HMPv35sub2r  <- transform_sample_counts(HMPv35sub2sub, function(x) x / sum(x))
#class(HMPv35sub2r)
HMPv35sub2fr <- filter_taxa(HMPv35sub2r, function(x) mean(x) > 1e-5, TRUE)
HMPv35sub2frbac = subset_taxa(HMPv35sub2fr, Phylum=="Bacteroidetes")
```


####Problem 5
Using your HMPv35sub2frbac object, what is the distribution of the top 20 OTU's?

```{r}
ntaxa(HMPv35sub2frbac)
par(mar = c(10, 4, 4, 2) + 0.1)
N <- 20
barplot(sort(taxa_sums(HMPv35sub2frbac), TRUE)[1:N]/nsamples(HMPv35sub2frbac), las=2)
```


####Problem 6

Plot sample abundance by body site for your object HMPv35sub2frbac

```{r}
title <- "Bar Plot; by site; Bacteroidetes only"
plot_bar(HMPv35sub2frbac, "HMPbodysubsite", "Abundance", title=title)
```


Let's try to see if there is something more to differentiate here beyond the black blobs.

```{r}



```

####Problem 7

You try it with your HMPv35sub2frbac object

```{r}
title <- "Well, that didn't work..."
plot_bar(HMPv35sub2frbac, "HMPbodysubsite", "Abundance", "Phylum", title=title)
```


We can use the techniques of network science to illustrate how similar or distant samples are.

Using our filtered object with all phyla, we use the `plot_net` function to illustrate the "proximity" (or similarity) of samples, while denoting site and the sex of the participant.

```{r}
plot_net(HMPv35sub2fr, maxdist = 0.3, color = "HMPbodysubsite", shape="sex")
```

Let's redo switching which variable is colored and which variable is differentiated by shape.

```{r}
plot_net(HMPv35sub2fr, maxdist = 0.3, shape = "HMPbodysubsite", color="sex")
```
####Problem 8

Which method of display do you like best and why?

```{r answer}
#Place your answer here as another comment.
# Since we only have one body site, using color to identify body site is not beneficial. Therefore, in this case, I prefer the latter method because it highlights the only differentiating node characteristic in the graph, sex. However, if we had two body sites, it would likely be more beneficial to differentiate body site by color, since that would likely be our variable of interest. In our current, single body site data subset, we could use both shape AND color to make the sex characteristic really pop out. Then, to improve the aesthetics, let's make the nodes larger, and organize it into a circle.
plot_net(HMPv35sub2fr, maxdist = 0.3, shape = "sex", point_size = 7, color="sex", laymeth="circle")
```