---
title: "NRSG 741 Homework 8"
author: "Tommy Flynn"
date: "4/11/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(class)
library(rpart)
library(NHANES)
library(RColorBrewer)
library(plot3D)
library(parallel)
library(randomForestSRC)
library(ggRandomForests)
library(mosaic)
```

K-nearest neighbor
Let's try a variation on the NHANES data set again.
  
```{r, echo=TRUE}
# Create the NHANES dataset again
people <- NHANES %>% dplyr::select(Age, Gender, Diabetes, BMI, HHIncome, PhysActive, SleepTrouble)%>%
  mutate(Gender = as.numeric(Gender), Diabetes = as.numeric(Diabetes), BMI,HHIncome = as.numeric(HHIncome),PhysActive = as.numeric(PhysActive)) %>%
  filter(!is.na(Age), !is.na(Gender), !is.na(Diabetes), !is.na(BMI), !is.na(HHIncome), !is.na(PhysActive), !is.na(SleepTrouble))
lut <- c("Yes" = "1", "No" = "0")
people$SleepTrouble <- as.numeric(lut[people$SleepTrouble])

#check the subset
glimpse(people)
```
Create the NHANES dataset again, just like we did in class, only using sleep trouble (variable name = SleepTrouble) as the dependent variable, instead of SleepTrouble. (I'm assuming you meann instead of Diabetes?) 
  
Problem 1
=========
What is the marginal distribution of sleep trouble?
```{r Problem 1}
# What is the marginal distribution of sleep trouble?
knitr::kable(tally(~ SleepTrouble, data = people, format = "percent"))
```



Problem 2
=========
Apply the k-nearest neighbor procedure to predict SleepTrouble from the other covariates, as we did for SleepTrouble. Use k = 1, 3, 5, and 20.  


```{r}
# Apply knn procedure to predict SleepTrouble

# Let's try different values of k to see how that affects performance
knn.1 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 1)
knn.3 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 3)
knn.5 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 5)
knn.20 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 20)
```

Now let's see how well these classifiers work overall

Problem 3
=========
```{r}
# Calculate the percent predicted correctly
100*sum(people$SleepTrouble == knn.1)/length(knn.1)
100*sum(people$SleepTrouble == knn.3)/length(knn.3)
100*sum(people$SleepTrouble == knn.5)/length(knn.5)
100*sum(people$SleepTrouble == knn.20)/length(knn.20)
```

Problem 4
=========
What about success overall?

```{r}
# Another way to look at success rate against increasing k
table(knn.1, people$SleepTrouble)
table(knn.3, people$SleepTrouble)
table(knn.5, people$SleepTrouble)
table(knn.20, people$SleepTrouble)
```

