---
title: "HW4"
author: "Vicki Hertzberg"
date: "2/17/2018"
output: html_document
---

```{r setup chunk 0, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(stringi)
```

####Problem 1.

Suppose you have another vector vText as follows:

```{r Problem 1}

vText <- c("google", "logo", "dig", "blog", "boogie")

```

You want to match `g`, `og`, `go`, or `ogo` and replace with `.`.

Write the R code that will make that happen.

####Answer to Problem 1.

```{r Answer 1}
pattern <- 'o?go?'
gsub(pattern, '.', vText)
```

###Section 2.

You have 3 strings of text that you wish to merge. One way to do this is to use the `paste` function.

```{r Intro 2}
x <- "I AM SAM. I AM SAM. SAM I AM."
y <- "THAT SAM-I-AM! THAT SAM-I-AM! I DO NOT LIKE THAT SAM-I-AM!"
z <- "DO YOU LIKE GREEN EGGS AND HAM?"
paste(x, y, z, collapse = NULL)
```

Extra credit: What is the difference if you use the `paste0` function instead of the `paste` function above?
>```past0(x, y, z, collapse = NULL)``` omits the space between character vectors.

####Problem 2.

Suppose that you now have 4 lines of text as follows:

```{r Problem 2}
W <- "Hey Diddle Diddle, the cat and the fiddle,"
X <- "The cow jumped over the moon."
Y <- "The little boy laughed to see such a sport,"
Z <- "And the dish ran away with the spoon."
```

Write the R code below to merge these 3 strings.

####Answer to Problem 2.

```{r Answer 2}
paste(W, X, Y, Z, collapse = NULL)
```

####Problem 3.

We now want to concatenate our 4 vectors and NA. Do this using both methods.

```{r Problem 3}

W <- "Hey Diddle Diddle, the cat and the fiddle,"
X <- "The cow jumped over the moon."
Y <- "The little boy laughed to see such a sport,"
Z <- "And the dish ran away with the spoon."

```

####Answer to Problem 3.

```{r Answer 3}

paste(W, X, Y, Z, NA, collapse = NULL)
str_c(W, X, Y, Z, " NA", collapse = NULL)
```

####Problem 4. 
Suppose Melinda Higgins wants to extract the last *6* letters of her name.

```{r Problem 4}
herName <- "Melinda Higgins"
```

Write the code below to extract the last 6 letters of her name.

####Answer to Problem 4.

```{r Answer 4}
Length <- str_length(herName)
last6letters <- str_sub(herName, Length-5, Length)
last6letters
```

####Problem 5.

I want to separate the following string into separate words:

```{r Problem 5}

myNewString <- "Now_is_the_time_for_all_good_men_to_come_to_the_aid_of_their_country"

```

Split this new string into separate words:

####Answer to Problem 5.

```{r Answer 5}

mySeparatedString <- str_split(myNewString, "_")
mySeparatedString
```

####Problem 6. 

Suppose we wanted to split off the first "word" from `myNewString`. Again, we have 

```{r Problem 6}

myNewString <- "Now_is_the_time_for_all_good_men_to_come_to_the_aid_of_their_country"

```

Split off the first word but leave the rest intact.

####Answer 6.

```{r Answer 6}

myNewSplitSpring <- str_split(myNewString, "_", n=2)
myNewSplitSpring
```

####Problem 7.

```{r}
yourNewString <- "Now is the time for all good men to come to the aid of their country"
```

Use the `stri_count_words` function as above to count the number of distinct words in `yourNewString`.

####Answer 7.

```{r Answer 7}
stri_count_words(yourNewString)
```

####Problem 8.

Suppose you have string listing famouse nurses and you want to find the duplicates. Here is the list:

```{r Problem 8}
nurses <-c("Nightingale", "Barton", "Dix", "Sanger", "Barton", "Woodruff", "Lincoln", "Dix", "Peplau")
```

####Answer 8.

```{r Answer 8}

nurses[stri_duplicated(nurses)]

```

####Problem 9.

Suppose we create the object `DIGITS` as follows:

```{r Problem 9}
DIGITS <- c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9")
```

How can we form the string `0_1-2_3-4_5-6_7-8_9-'?

####Answer 9.

```{r Answer 9}
stri_join(DIGITS, separators = c("_","-"), collapse = "")
```

####Problem 10

Using the original pun, replace `his` with `her` and ` he ` with ` she `:

```{r Problem 10}
pun<- "A statistician can have his head in an oven and his feet in ice, and he will say that on the average he feels fine"
```

####Answer 10 

Note that the word `head` also starts with `he` but we don't want to substitute `she` into there.

```{r Answer 10}

punModified <- stri_replace_all_fixed(pun, c("his", " he "), c("her", " she "), vectorize_all = FALSE)
punModified
```
